Enforced Invariant Confluence

### 2018-04-30 doc/paper/sections/related_work.tex
Shrunk paper.

\textbf{CRDTs.}
CRDTs~\cite{shapiro2011conflict, shapiro2011comprehensive} are distributed
semilattices with inflationary update methods. Due to their algebraic
properties, CRDTs can be replicated with strong eventual consistency without
the need for any coordination. Our definition of distributed objects and our
\invariantconfluence{} system model are inspired directly by the corresponding
definitions and system models in~\cite{shapiro2011conflict}. Also, an
\invariantconfluent{} object does not necessarily have to be eventually
consistent, so it is natural (though not necessary) to use CRDTs as
\invariantconfluent{} distributed objects, achieving a combination of eventual
consistency and invariant preservation. Our criteria in
\thmref{LatticeProperty} also borrow ideas from CRDTs, exploiting the nice
algebraic properties of semilattices.

\textbf{CALM Theorem.}
Bloom~\cite{alvaro2010boom, alvaro2011consistency, conway2012logic} and its
formalism, Dedalus~\cite{alvaro2011dedalus, alvaro2013declarative}, are
declarative Datalog-based programming languages that are designed to program
distributed systems. The accompanying CALM
theorem~\cite{hellerstein2010declarative, ameloot2013relational} states that if
a program can be written in the monotone fragment of these languages, then
there exists a coordination-free implementation of the program.  The CALM
theorem provides guarantees about the outputs of a program, but it does not
guarantee that invariants are maintained throughout the duration of an
execution. Moreover, Bloom and Dedalus are general purpose programming
languages that can be used to implement a variety of distributed systems (e.g.
a sharded database) which are outside of the scope of \invariantconfluence{}.

>>>>

% \textbf{CRDTs.}
% CRDTs~\cite{shapiro2011conflict, shapiro2011comprehensive} are distributed
% semilattices with inflationary update methods. Due to their algebraic
% properties, CRDTs can be replicated with strong eventual consistency without
% the need for any coordination. Our definition of distributed objects and our
% \invariantconfluence{} system model are inspired directly by the corresponding
% definitions and system models in~\cite{shapiro2011conflict}. Also, an
% \invariantconfluent{} object does not necessarily have to be eventually
% consistent, so it is natural (though not necessary) to use CRDTs as
% \invariantconfluent{} distributed objects, achieving a combination of eventual
% consistency and invariant preservation. Our criteria in
% \thmref{LatticeProperty} also borrow ideas from CRDTs, exploiting the nice
% algebraic properties of semilattices.

\textbf{CALM Theorem.}
Bloom~\cite{alvaro2010boom, alvaro2011consistency, conway2012logic} and its
formalism, Dedalus~\cite{alvaro2011dedalus, alvaro2013declarative}, are
declarative Datalog-based programming languages that are designed to program
distributed systems. The accompanying CALM
theorem~\cite{hellerstein2010declarative, ameloot2013relational} states that if
a program can be written in the monotone fragment of these languages, then
there exists a coordination-free implementation of the program.  The CALM
theorem provides guarantees about the outputs of a program, but it does not
guarantee that invariants are maintained throughout the duration of an
execution. Moreover, Bloom and Dedalus are general purpose programming
languages that can be used to implement a variety of distributed systems which
are outside of the scope of \invariantconfluence{}.
